---
title: "Analysis_big_cars_epa"
author: "Serdar Korur"
date: "10/21/2019"
output: html_document
---
```{r import packages & data}
library(tidyverse) # ggplot2, dplyr, tidyr, readr, 
                   # purrr, tibble, stringr, forcats
big_epa_cars <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-10-15/big_epa_cars.csv")
big_epa_cars %>% View()

# Make it alphebeticall like in data dictionary
big_epa_cars_alp <- big_epa_cars %>% select(sort(colnames(big_epa_cars)))
big_epa_cars_alp %>%  view()

# Check the columns
big_epa_cars_alp %>% count(atvType, sort =TRUE)
```


```{r size of the data}
# Dimension of the data
dim(big_epa_cars)
names(big_epa_cars)
str(big_epa_cars)
```


```{r examine data}
# Examine single columns
big_epa_cars %>% select(fuelType) %>% table()
big_epa_cars %>% select(trany) %>% table()
big_epa_cars %>% select(lv4) %>% table()

# Evolutuion of Automatic vs Manual cars

# Plot fueltype evolution in years
# check 2d box plot (weight by n)
p <- ggplot(big_epa_cars, aes(x=fuelType, y =year)) + geom_point() + theme(axis.text.x = element_text(angle = 45, hjust = 1))
p
```

# Premium fuel cars dominate after 2000 and after 2010 Electric cars start to get popular
```{r examine data}
# Using Varwidth
p <- ggplot(big_epa_cars, aes(x=fuelType, y =year)) + geom_boxplot(varwidth=TRUE) + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + coord_flip()
p
```



```{r check out those}
# Checking out
fct_reorder()    ---forcats package
fct_lump() ?
coord_flip

```


**tidy:** constructs a data frame that summarizes the model’s statistical findings. This includes coefficients and p-values for each term in a regression, per-cluster information in clustering applications, or per-test information for multtest functions.

**augment:** add columns to the original data that was modeled. This includes predictions, residuals, and cluster assignments.

**glance:** construct a concise one-row summary of the model. This typically contains values such as R^2, adjusted R^2, and residual standard error that are computed once for the entire model.